Effects of CHILDREN's programs

### 2020-02-26 paper.Rnw
new function weightOuliers
moved all library calls from Gather and other data files to MakeGather

continued MakeAnalysis

finished first factor analysis

In their surveys, CHILDREN asks about two variables in both programs. These are the share of beneficiaries that are believed to have increased their self-worth and to have ehanced their everyday expertise. This feature could potentially allow us to compare the two programs regarding their realtive effectiveness. Like always, we standardize the two outcome variables. As before, we can only make associational claims. We invariably find no clear-cut relationship between the subsidy per beneficiary and the two outcomes. In fact, no coefficent is statistically significantly differnent from zero at any of the usual levels.

Tables \ref{SelfworthRegressions} and \ref{DayToDaySkillsRegressions} present the null results.

@@

>>>>

In their surveys, CHILDREN asks about two variables in both programs. These are the share of beneficiaries that are believed to have increased their self-worth and to have ehanced their everyday expertise. This feature could potentially allow us to compare the two programs regarding their realtive effectiveness. Like always, we standardize the two outcome variables. As before, we can only make associational claims. We invariably find no clear-cut relationship between the subsidy per beneficiary and the two outcomes. In fact, no coefficent is statistically significantly differnent from zero at any of the usual levels. 
The four variables are recorded for each year in which the program was operative.
Tables \ref{SelfworthRegressions} and \ref{DayToDaySkillsRegressions} present the null results.

@@

We use imputed data set.

we use the orthogonal rotation technique Varimax, which is recommended in Price (2017, p. 307) when the goal of analysis is to "minimize complexity of factors by maximizing variance of loadings on each factor" 
We estimate factor scores with the Bartlett method, which is similar to a Maximum Likekelihood estimation, and presented as the most convential one in Eid and Schmidt (2010, p. 291)
We use maximum likelihood as factoring method
